Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-14 ms.qmd
Fixed some code

if(rerun){
  # More realistic model 
  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 + max_temp_c| spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data)

@@

  # Save model
  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")
  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")

>>>>

if(rerun){
  # More realistic model 
  model2.4 <- metafor::rma.mv(effect_size ~  max_temp_c + c_accl_time + type*habitat*life.hist, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 + max_temp_c| spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data)
  # Save model
  saveRDS(model2.4, file = "./output/models/lnCVRQ10_2.4")

@@

  # Save model
  saveRDS(model2.4_bayes, file = "./output/models/lnCVRQ10_2.4_bayes")
